### 2021-04-08 article/paper_eng.tex
fixed title

\begin{center}
    \huge\textbf{Training Inhibitory Connections Between Local Receptive Fields in Spiking Neural Networks}\\
\end{center}

@@

\addcontentsline{toc}{section}{Conclusion}
\section*{Conclusion}
It was shown that for the problem of pattern recognition on the MNIST dataset, the locally connected architecture with competition is superior to the convolutional one with an equal number of parameters.
It was also shown that training inhibitory weights can slightly improve the quality of the model, and in the resulting distribution of inhibitory weights, both with high values (strong competition) and low (cooperation) values of weights are important.

>>>>

\begin{center}
    \huge\textbf{Training Inhibitory Connections Between Receptive Fields in a Locally Connected Spiking Neural Network}\\
\end{center}

@@

\addcontentsline{toc}{section}{Conclusion}
\section*{Conclusion}
It was shown that for the problem of pattern recognition on the MNIST dataset, the locally connected architecture with competition is superior to the convolutional one with an equal number of parameters.
It was also shown that training inhibitory weights can slightly improve the quality of the model, and in the resulting distribution of inhibitory weights, both weights with high (strong competition) and low (cooperation) values are important..
